---
title: "Running EcoAssocNet from R"
output:
  html_document:
    df_print: paged
---

In the following chunk, changer the root.dir by your current working directory.
```{r setup}
knitr::opts_knit$set(root.dir = '~/EcoAssocNet/Source code/')
```

### Configuration
First, configure RStudio to use the virtual environments where you installed EcoAssocNet and its dependencies.
The following command does that, py_config() shows you the version of Python used by reticulate. 

```{r, warning=FALSE}
library(reticulate)
use_condaenv("phd")
py_config()
```

### Importing ecoassocnet
We provide the following script which contains bundles functions for performing usual data processing pipelines followed  by the training procedure specific to the proposed framework.
```{r, warning=FALSE, echo=FALSE}
source_python("ecoassocnet/run_ecoassoc.py")
### Or 
#ea <- import(ecoassocnet.run_ecoassoc)
```

### Loading and preprocessing data
```{r, warning=FALSE}
training_output=run_ecoassoc(folder_data="doc/examples/Aravo/data/",file_env="env.csv",file_count="occur.csv",
                 training_config_file="doc/examples/Aravo/config/association_learning.ini",
                 name_dataset="aravo",target="count",
                 num_vars=c("Slope","PhysD","Snow"),cat_vars=c("Aspect","Form","ZoogD"),
                num_std="minmax",cat_trt="onehot",
                 offset_mode="avgnz",verbose=0,
                 meth="stratified",p=0.8)

model=training_output$model
data=training_output$data
metadata=training_output$metadata
```

### Retrieving and filtering associations
```{r}
assoc_mat=model$compute_associations(save=FALSE,norm=TRUE)

selected_assoc_mat=apply_biogeo_filter(assoc_df=assoc_mat,occur=data$occur,weights=model$mle$final_weights,thoccur=0,thass=0.75,thresp=0.5,names=metadata$names)
```

### Visualization
```{r}
util <-import("ecoassocnet.Util.Util")
### Loading the final association matrix 
assoc <- read.csv2('doc/examples/Aravo/results/plant_associations.csv',row.names = 1)
util$plot_association(mat=assoc,fileout='doc/examples/Aravo/results/assoc.pdf')
util$plot_assoc_clustered(assoc,file='doc/examples/Aravo/results/assoc_clustered.pdf')
```

